--- 
title: "Material for ESL/EFL Instruction"
author: "Drake Asberry"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a working example of teaching resources that I have compiled over my years of teaching experience. The output format for this example is bookdown::gitbook."
---

# Introduction

This is a website started in December 2020 as a project I started to document resources I have created or found useful over the years. The intent is that it will continue to grow and evolve while remaining portable because traveling with all these physical items is too cumbersome. I hope that others will find the resources here useful as well.

If you would like to contribute to this site, please submit a pull request via the [github repository](https://github.com/drakeasberry/english_learning_resources).


```{r eval=FALSE}
# The **bookdown** package can be installed from CRAN or Github:
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
